О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Cosmetics
Code cosmetics
Add construction with unique minimum edge

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta|=l$ and $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = n^2 + 1$.
	Then $l \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$
	.
\end{lemma}

@@

	(see~\cite[]{erdos1945integral} for details).

	Summing up the cases above, we get the following estimate:
	\begin{equation}
		\label{eq:estimate_n_varphi_n_squared}
		n \leq 4 b^2 \varphi_{n-1}^2 - 4 + \gamma_2 b + 6
		.
	\end{equation}
	Observation~\ref{varphi_n_where_n_geq_21492} turns estimate~\eqref{eq:estimate_n_varphi_n_squared}
	into the following:
	\begin{equation}
		\label{eq:estimate_n_sqrt_n-2}
		n-2 \leq 4 b^2 \frac{\beta^2}{n-2} + \gamma_2 b
		,
	\end{equation}
	which obviously leads to inequality
	\begin{equation}
		1 \leq 4\beta^2 \left(\frac{b}{n-2}\right)^2  + \gamma_2 \frac{b}{n-2}
		.
	\end{equation}
	Let us denote $\lambda = b/(n-2)$ and solve the following square inequality with respect to $\lambda$:
	\begin{equation}
		\label{eq:square_inequality_lambda}
		4\beta^2 \lambda^2  + \gamma_2 \lambda - 1 \geq 0
		.
	\end{equation}
	The discriminant is $\gamma_2^2 + 16 \cdot \beta^2$,
	so we obtain the following estimate:
	\begin{equation}
		\frac{b}{n-2} = \lambda \geq \frac{-\gamma_2 + \sqrt{\gamma_2^2 + 16 \cdot \beta^2}}{8\beta^2}
		.
	\end{equation}
	Calculating the expression above for our $\beta$ and $\gamma_2$, we conclude the proof.
\end{proof}

@@

TODO: construction with unique minimum edge?

@@

So, Conjecture~\ref{hyp:prime_planar} needs proof only for $m=2$.

>>>>

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta|=l$ and $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = n^2 + 1$.
	Then
	\begin{equation}
		l \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n
		.
	\end{equation}
\end{lemma}

@@

	(see~\cite{erdos1945integral} for details).
	Summing up the cases above, we get the following estimate:
	\begin{equation}
		\label{eq:estimate_n_varphi_n_squared}
		n \leq 4 b^2 \varphi_{n-1}^2 - 4 + \gamma_2 b + 6
		.
	\end{equation}
	Observation~\ref{varphi_n_where_n_geq_21492} turns estimate~\eqref{eq:estimate_n_varphi_n_squared}
	into the following:
	\begin{equation}
		\label{eq:estimate_n_sqrt_n-2}
		n-2 \leq 4 b^2 \frac{\beta^2}{n-2} + \gamma_2 b
		,
	\end{equation}
	which obviously leads to inequality
	\begin{equation}
		1 \leq 4\beta^2 \left(\frac{b}{n-2}\right)^2  + \gamma_2 \frac{b}{n-2}
		.
	\end{equation}
	Let us denote $\lambda = b/(n-2)$ and solve the following square inequality with respect to $\lambda$:
	\begin{equation}
		\label{eq:square_inequality_lambda}
		4\beta^2 \lambda^2  + \gamma_2 \lambda - 1 \geq 0
		.
	\end{equation}
	The discriminant is $\gamma_2^2 + 16 \cdot \beta^2$,
	so we obtain the following estimate:
	\begin{equation}
		\frac{b}{n-2} = \lambda \geq \frac{-\gamma_2 + \sqrt{\gamma_2^2 + 16 \cdot \beta^2}}{8\beta^2}
		.
	\end{equation}
	Calculating the expression above for our $\beta$ and $\gamma_2$, we conclude the proof.
\end{proof}

@@

@@

So, Conjecture~\ref{hyp:prime_planar} needs proof only for $m=2$.
For $m>2$, a bit more strong result can also be claimed.

\begin{theorem}
	For arbitrary integers $m > 2$, $n \geq m+1$, $d \geq 1$
	there exists a prime set $M\in\mathfrak{M}(m,n)$,
	such that for some $M_1, M_2\in M$ equality $|M_1 M_2| = d$ holds,
	the distance $d$ is minimal and occurs in $M$ only once.
\end{theorem}

\begin{proof}
	Exploit Construction~\ref{con:planar_set_with_minimeter_1} to get $M'\in \mathfrak{M}(2,n-m+2)$
	with $M'_1, M'_2 \in M'$ and $|M'_1 M'_2| = 1$.
	Dilate $M'$ to $M''$ in such a way that $M'_1$ and $M'_2$ turn into $M''_1$ and $M''_2$ resp.
	and $|M''_1 M''_2| = d$.
	Then ``blow up'' $M''$ to $M\in \mathfrak{M}(m,n)$ using a simplex of side length $d+1$.
	The greatest common divisor of $d$ and $d+1$ is $1$, so $M$ is prime.
\end{proof}
